Making Q-learning robust to time discretization

### 2019-01-17 paper/icml_drau/relatedworks.tex

Our approach largely builds on \cite{adv_upd}, who identified the
collapse of Q-learning for small time steps and suggested advantage
updating with proper $\deltat$ scalings as a solution.

@@

More recently, \cite{dueling_nets} also introduced a parameterization separating
the value and the advantage components of the Q-function. We additionally
introduce a natural scaling coeficient between the two, that strongly improves
the time discretization invariance properties.

>>>>

Our approach expands on \cite{adv_upd}, who identified the collapse of
Q-learning for small time steps and suggested as a solution the Advantage Updating
algorithm with proper $\deltat$ scalings for the $V$ part and the
advantage part; testing was only
done on a quadratic-linear problem. Using a different normalization step
for $A$ (which forgoes the need to learn the normalization itself, thanks
to the parameterization \eqref{eq:Aparam}), we test Advantage Updating
for the first time on a variety on RL environments using deep networks,
establishing Deep Advantage Updating as a viable algorithm in this
setting.  Additionally, we provide formal proofs for the collapse of
Q-learning when $\deltat\to 0$, and for the non-collapse of Advantage
Updating, in a general setting.

\TODO{Say that Actor-critic has no problem when $\deltat\to 0$?}

@@

More recently, \cite{dueling_nets} also introduced a parameterization separating
the value and the advantage components of the Q-function. Contrary to
\cite{advup}'s Advantage Updating, learning is still done in a standard
way on the $Q$-function obtained from adding these two components. Thus this
approach reparameterizes $Q$ but does not introduce the proper scalings
and does not result in an invariant algorithm for small $\deltat$.%We additionally
%introduce a natural scaling coeficient between the two, that strongly improves
%the time discretization invariance properties.
